Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex

\newcommand{\shortreply}[2][]{\medskip \noindent \textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip}

% Numbering figures according to reviewers
\renewcommand{\thefigure}{\thereviewer{}.\arabic{figure}}

\begin{document}

\section*{Response to the Reviewers}
% General intro text goes here
We thank the reviewers for their critical assessment and insightful comments on our work.
%
We have made extensive modifications to our manuscript, including adding more experiments and improving the presentation.
%
In the following, we first summarize the major changes we made.
%
%We also prepare an \emph{annotated version} for our revised manuscript.
%
%In the annotated version, changes corresponding to each point are all highlighted by red squares.

@@

\subsection*{Summary of Changes}

\begin{enumerate}
\item According to Reviewer 1's comments, we have added experiments on the performance bottleneck analysis of GNN inference.
%
We added experiments on how the hyper-parameters of GNNs affect the elapsed time and the memory usage of inference in Section 4.1.2 ``Effects on Inference Time'' and Section 4.1.3 ``Effects on Peak Memory Usage'', respectively.
%
We added time breakdown analysis of GNN inference in Section 4.2.4.
%
We also presented the memory usage analysis of GNN inference in Section 4.3.2.
%
The performance bottlenecks of sample-based inference were analyzed in Section 4.4.2.

\item According to the Reviewer 2's comments, we have added experiments on how the model complexity and the sampling techniques affect the accuracy of GNNs.
%
Specifically, we evaluated the effects of hyper-parameters of GNNs on accuracy in Section 4.1.4.
%
We also compared the accuracy of the four typical GNNs in that section.
%
We analyzed the effects of the sampling techniques on accuracy in Section 4.4.3.

\item We have adjusted the abstract, Section 1 ``Introduction'', and Section 5 ``Insights'' according to the new findings on inference time and accuracy.

\item We have polished the presentation of our manuscript.
%
We unified the symbol usage through the manuscript and added a table to summarize the frequently-used symbols.
%
We improved the description of the sub-layer concept in Section 2.1 and Section 2.2.
%
We also replotted some figures to improve readability.

We then respond to the concerns of reviewers point by point as follows.

@@

% R1Q1
\begin{point}
	There are lots of symbols in this paper. Some symbols are reused and confusing, such as s denotes sub-layers or edge features.
\end{point}

% Our reply
\begin{reply}
    We apologize for the confusing use of symbols.
    %
    To clarify the symbol usage, we have unified the usage of symbols in the revised manuscript.
    %
    After revision, each symbol only represents one meaning.

    Specifically, we use $\boldsymbol{s}$ to represent aggregated vectors in graph neurons.
    %
    We use $\boldsymbol{s}^l_x$ to denote the aggregated vector of the graph neuron corresponding to the vertex $v_x$ in the GNN layer $l$.
    %
    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents the aggregated vector of $v_x$ in the $i$-th sub-layer.
    %
    As for edges and their feature vectors, we use $e_{y,x}$ to represent an edge pointing from $v_y$ to $v_x$ and we use $\boldsymbol{e}_{y,x}$ to represent its feature vector.

    In order to facilitate readers to quickly locate the meaning of  symbols, we have added Table 1 at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised manuscript.

@@

    \begin{figure}[h]
            \centering
            \subfloat[\texttt{amp}\label{fig:exp_graphsage_sampling_accuracy_on_amp}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
            \subfloat[\texttt{amc}\label{fig:exp_graphsage_sampling_accuracy_on_amc}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
            \subfloat[\texttt{fli}\label{fig:exp_graphsage_sampling_accuracy_on_fli}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
            \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
            \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
        \end{figure}

        \begin{figure}[h]
            \centering
            \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
            %
            \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
            %
            \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
            \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
            \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
        \end{figure}

    The results indicate that the relationships between batch size and test accuracy are complex, especially for the neighbor sampler.
    %
    A larger batch size does not always bring higher accuracy, like GAT in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_fli}. 
    %
    Our observations are similar to [\cite{zeng2020_graphsaint}].
    %
    How to automatically select a proper batch size is a topic worth studying.
\end{reply}

@@

\begin{point}
    Hope authors supplement the effect of sampling and GNNs on accuracy while comparing different complexity of model and sampling methods.
\end{point}

\begin{reply}

    We are grateful for your insightful suggestion.
    %
    As suggested, we additionally evaluate the effects of model complexity on accuracy in Section 4.1 ``Effects of Hyper-parameters on Performance'' in the revised manuscript.
    %
    We add discussion on how the hyper-parameters of GNNs affect the accuracy.
    %
    We also compare the test accuracy of different GNN models on the same dataset.

    We also additionally evaluate the effects of sampling techniques on accuracy in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
    %
    We present the experimental results and related discussion in a new subsection Section 4.4.3 ``Effects on Accuracy''.
\end{reply}

\bibliographystyle{apalike}
\bibliography{../gnnref.bib}

### 2020-12-26 NEUROC/sec7-conclusion.tex

This work is funded in part by National Key R\&D Program of China [grant number 2019YFC1711000]; China NSF Grants [grant number U1811461]; Jiangsu Province Industry Support Program [grant number BE2017155]; Natural Science Foundation of Jiangsu Province [grant number BK20170651]; Collaborative Innovation Center of Novel Software Technology and Industrialization; and the program B for Outstanding PhD candidate of Nanjing University.

>>>>

This work is funded in part by the National Key R\&D Program of China [grant number 2019YFC1711000], the China NSF Grants [grant number U1811461, 62072230], and the Collaborative Innovation Center of Novel Software Technology and Industrialization; and the program B for Outstanding PhD candidate of Nanjing University.
